---
title: "`CHNS`: A Data Package for Chinese Health and Nutrition Survey Data"
author: "Betty Pu and Junru Wu"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{`CHNS`: A Data Package for Chinese Health and Nutrition Survey Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: rmarkdown::html_vignette
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warnings = FALSE,
  errors = FALSE
)
```

```{r setup, include=FALSE}
library(chns)
library(dplyr)
library(leafletCN)
```

## Summany

The `CHNS` package contains data from the [Chinese Health and Nutrition Survey](https://www.cpc.unc.edu/projects/china/data) with 10 years of survey data over the period of 1989 to 2015. The users can use the cleaned data sets and functions for data analysis and visualization.\

The package includes two data set that includes individual-level survey data of 10 specific years over the period of 1989 - 2015.\

There are currently three functions inside the package:\

- `real_income`: takes in a numeric year value and returns a data frame with real income adjusted for inflation.\

- `num_of_children`: takes in a numeric year value and returns a data frame with child births, child deaths, and total children up to the input year.\

- `map_income`: takes in a numeric year value and returns a map of China with province-level average annual income mapped on the surveyed provinces.\

This package would be a useful tool for social science researchers interested in policy analysis in China. Additionally, it is also an easy tool for data analysis and visualization for anyone interested in CHNS.


## Datasets Included
- `indinc_10_clean`: A data set that includes 88166 survey data entries from 1989 - 2015. IDind is individual's ID, wave is the survey year, and indwage is annual nominal income. Negative and N/A values are recorded as 0 in the cleaned data set.

- `emw_12_clean`: A data set that includes 26616 survey data entries from 1989 - 2015 with Individual ID, survey year, number of child died and number of child births for women; negative and N/A values are recorded as 0 in the data set.

- `map_dat_clean`: A simple data set with province-level average annual income, survey year, province names in both English and Chinese, and categories of income that is used for mapping; wage_mean_k is annual average income in unit of ¥1,000, and mage_mean_cat are manually constructed categories in unit of ¥1,000 for mapping.


## What does the data look like?

Here's the first 5 rows of the `indinc_10_clean` data set.

```{r}
head (indinc_10_clean)
```


## What can we do with this package?

We can use this package to analyze and visualize CHNS data. 

We can use these functions  as a preliminary data preparing tool to answer research questions regarding China’s social-economic conditions such as:

Below are some examples of the existing functionality the package provides, including data wrangling and data visualization techniques.

```{r, message=FALSE, warning=FALSE}
library(chns)
library(dplyr)
library(leafletCN)
```

- Example 1: Get Real Income with selected base year.

This is a basic example for `real_income()` that returns a tibble with income weighted over inflation for the selected base year.

`real_income(base_year)`: This function calculates the deflated/inflated real income based on the selected survey year. 

```{r}
real_income(base_year=1989) 
```

- Example 2: Get Number of Children a women has up to an inputted year.

`num_of_children(base_year)`: This function returns a data frame with the number of children a woman had up to an inputted year. 

```{r}
num_of_children(year = 2006) 
```

Here is the function for data visualization: `map_income()`

- Example 3: Get a map to get an overview of province-level average income.

`map_income(year)`: This function would potentially map the population density by province on the map for the selected year.

```{r}
map_income(year = 2006) 
```



